reactablefmtr and title size issue?

### 2021-08-20 _post/2021-08-19-reactablefmtr-and-title-size-issue/reactablefmtr-and-title-size-issue.Rmd
add frmtr post

---
title: "reactablefmtr and title size issue?"
description: |
  A short description of the post.
author:
  - name: Roland Schmidt
    url: https://werk.statt.codes
date: 08-19-2021
output:
  distill::distill_article:
    self_contained: false
---

>>>>

---
title: "reactablefmtr and title size issue?"
description: |
  A short description of the post.
author:  
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693
date: 08-19-2021
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: false
    code_folding: TRUE
---
